---
title: "Module Input Output"
author: "Zhengjia Wang"
date: "2/7/2019"
output: html_document
runtime: shiny
---

<style>
.shiny-frame{
  min-width: 100vw;
  height: 80vh;
  position: relative;
  transform: translateX(-50%);
  left: 50%;
  margin-right: -99vw
}
</style>

```{r setup, include=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r debug, message=FALSE, echo=FALSE, warning=FALSE}
junk = capture.output({..env = ravebuiltins::dev_ravebuiltins()})
..env$cat2 = function(...){}
## Load subject for debugging
# ..env$mount_demo_subject()
..env$view_layout('power_explorer')
```


This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r module_inputs, eval=FALSE}
#  ----------------------  Initializing Global variables -----------------------
load_scripts(
  'inst/modules/power_explorer/3d_viewer.R'
)

define_initialization({
  ##
  ## Make sure power (referenced) exists
  ## with the following line, RAVE will pop up a dialogue if 
  ## power is not loaded and ask users to load data
  ## 
  rave_checks('power referenced')
  
  ##
  ## Get referenced power (Wavelet power)
  ## 
  power = module_tools$get_power(referenced = TRUE)
  
  ## Shared variables
  frequencies = preload_info$frequencies
  time_points = preload_info$time_points
  electrodes = preload_info$electrodes
  epoch_data = module_tools$get_meta('trials')
})




#  ---------------------------------  Inputs -----------------------------------
# Define inputs

# Select from multiple choices, 
define_input(
  definition = textInput('electrode_text', 'Electrodes', value = "", placeholder = '1-5,8,11-20'),
  init_args = c('label', 'value'),
  init_expr = {
    last_input = cache_input('electrode_text', val = as.character(electrodes[1]))
    e = dipsaus::parse_svec(last_input)
    e = e[e %in% electrodes]
    if(!length(e)){
      e = electrodes[1]
    }
    value = dipsaus::deparse_svec(e)
    label = 'Electrodes (' %&% deparse_selections(electrodes) %&% ')'
  }
)

define_input(
  definition = customizedUI(inputId = 'input_customized')
)

define_input(
  definition = sliderInput('FREQUENCY', 'Frequency', min = 1, max = 200, value = c(1,200), step = 1, round = 1),
  init_args = c('min', 'max', 'value'),
  init_expr = {
    min = floor(min(frequencies))
    max = ceiling(max(frequencies))
    value = cache_input('FREQUENCY', c(min, max))
  }
)

define_input(
  definition = sliderInput('TIME_RANGE', 'Analysis', min = 0, max = 1, value = c(0,1), step = 0.01, round = -2),
  init_args = c('min', 'max', 'value'),
  init_expr = {
    min = min(time_points)
    max = max(time_points)
    value = cache_input('TIME_RANGE', c(0, max(time_points)))
  }
)

define_input(
  definition = sliderInput('BASELINE', 'Baseline', min = 0, max = 1, value = c(0,1), step = 0.01, round = -2),
  init_args = c('min', 'max', 'value'),
  init_expr = {
    min = min(time_points)
    max = max(time_points)
    value = cache_input('BASELINE', c(min(time_points), 0))
  }
)

define_input(
  definition = selectInput('combine_method', 'Electrode Transforms',
                           choices = c('none', 'z-score', 'max-scale', '0-1 scale', 'rank'), 
                           multiple = F, selected = 'none')
)


define_input(
  definition = selectInput('reference_type', 'Transform Reference',
                           choices = c('Trial', 'Trial type', 'Active trial types', 'All trials'), 
                           selected='Trial')
)

define_input(
  definition = selectInput('reference_group', 'Reference Group',
                           choices = c('Per Electrode', 'All Electrodes'), selected = 'Per Electrode')
)

define_input(
  definition = numericInput('max_zlim', 'Maximum Plot Value', value = 0, min = 0, step = 1)
)
define_input(
  definition = checkboxInput('log_scale', 'Log Freq')
)
define_input(
  definition = checkboxInput('sort_trials_by_type', 'Sort Trials')
)



define_input(
  definition = compoundInput(
    inputId = 'GROUPS', prefix= 'Group', inital_ncomp = 1, components = {
      textInput('GROUP_NAME', 'Name', value = '', placeholder = 'Name')
      selectInput('GROUP', ' ', choices = '', multiple = TRUE)
    }),
  init_args = c('initialize', 'value'),
  init_expr = {
    trials = preload_info$condition
    initialize = list(
      GROUP = list(
        choices = unique(trials)
      )
    )
    value = cache_input('GROUPS', list(
      list(
        GROUP = list(trials),
        GROUP_NAME = 'All Conditions'
      )
    ))
  }
)


# Define layouts if exists
input_layout = list(
  '[#cccccc]Electrodes' = list(
    c('electrode_text'),
    c('combine_method'),
    c('reference_type', 'reference_group')
  ),
  '[#99ccff]Trial Selector' = list(
    'GROUPS'
  ),
  'Analysis Settings' = list(
    'FREQUENCY',
    'BASELINE',
    'TIME_RANGE'
  ),
  '[-][#33aaff]Export Options' = list(),
  '[-]Plotting' = list(
    c('log_scale', 'sort_trials_by_type', 'collapse_using_median'),
    c('max_zlim')
  )
)

```

```{r module outputs, eval=FALSE}
# Define Outputs
define_output(
  definition = plotOutput(outputId = 'heat_map_plot'),
  title = 'Heat Map (Collapse trial)',
  width = 12,
  order = 1
)

define_output(
  definition = plotOutput('by_trial_heat_map'),
  title = 'Activity over time by trial (Collapse freq)',
  width = 12,
  order = 2
)

define_output(
  definition = plotOutput('over_time_plot'),
  title = 'Collapse freq+trial',
  width = 8,
  order = 4
)

define_output(
  definition = plotOutput(outputId = 'windowed_comparison_plot'),
  title = 'Collapse time+freq',
  width = 4,
  order = 3
)

define_output(
  definition = customizedUI('viewer_3d'),
  title = '3D Viewer',
  width = 12,
  order = 5
)


# output_layout = list(
#   # 'Tabset One' = list(
#   #   'Multiple Output' = 'heat_map_plot'
#   # )
#   'Multiple Output' = 'heat_map_plot'
# )
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:


Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



